%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.6in,top=0.7in,right=0.6in,bottom=0.5in]{geometry} % Document margins

\name{Yifan Ge}
% \address{647 Lamont Ct, Campbell, CA 95008}
\address{\raisebox{-0.1\height}\faLinkedin \  \url{https://www.linkedin.com/in/yifange} \\ \raisebox{-0.1\height}\faGithub \ \url{https://www.github.com/yifange}}
\address{(408) 769-8746 \\ \href{mailto:yifange101@gmail.com}{yifange101@gmail.com}}

\begin{document}

\begin{rSection}{Summary}
Experienced Full-Stack Software Engineer with 10+ years of expertise in building scalable, intuitive, and accessible applications for both end users and developers. Adept at leading cross-functional teams, architecting robust frontend and backend solutions, and optimizing user experiences. Passionate about performance, accessibility, and modern web technologies.

\end{rSection}

\begin{rSection}{Technical Skills}
  \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
  Languages & JavaScript, TypeScript, Java, Python, Go, Swift, SQL \\
  Frontend & React, Angular, AngularJS, Webpack, Sass, CSS/HTML \\
  Backend \& APIs & gRPC, RESTful APIs, Node.js \\
  Infrastructure \& Tools & Google Cloud, Git, CI/CD \\
  Other & Machine Learning, Web Accessibility (a11y), Chrome Extensions
  \end{tabular}
\end{rSection}

\begin{rSection}{Professional Experience}

\begin{rSubsection}{Apple Inc}{Jan. 2022 - Present}{Senior Software Engineer}{Cupertino, CA}
\item Develop and maintain \textbf{iCloud.com} and various iCloud web services, optimizing performance for millions of active users.
\item \textbf{Project DRI} for iCloud Drive Web App, led a team of engineers, managing project planning and technical execution.
\item Designed and implemented visually rich, high-performance UIs while ensuring \textbf{seamless user experiences}.
\item Advocated for \textbf{web accessibility best practices}, improving usability for a diverse user base.
\item Collaborated with product, design, and backend teams to define, develop, and deliver core product features.
\item \textbf{Tech Stack}: React, TypeScript, Webpack, Node.js, Swift
\end{rSubsection}


\begin{rSubsection}{Google Inc.}{Nov. 2015 - Jan. 2022}{Software Engineer}{Mountain View, CA}
\item Full-stack developer on \textbf{Google Issue Tracker}, a widely-used project tracking tool for internal engineers and external developers managing projects for Android, Chrome, and Google Cloud Platform.
\item Designed and developed \textbf{user-friendly and accessible UI components} with Angular and TypeScript.
\item Built scalable \textbf{gRPC-based APIs and Java backend services}, improving system efficiency and performance
\item Led development of a \textbf{Chrome extension} with 13,000+ users, streamlining internal workflows.
\item Contributed to \textbf{Angular Material}, an open-source UI library widely adopted by frontend developers, enhancing accessibility and UI component usability.
\item \textbf{Tech Stack}: Angular, TypeScript, JavaScript, Java, Protobuf, Python, SQL, Sass, CSS, HTML

\end{rSubsection}

\begin{rSubsection}{Motorola Mobility}{Jul. 2014 - Aug. 2015}{Software Engineer}{Sunnyvale, CA}
\item Developed an \textbf{internal data analytics tool}, leading both frontend (AngularJS) and backend (Go) development.
\item Deployed and managed the application on \textbf{Google Cloud App Engine}, ensuring high availability and scalability.
\item \textbf{Tech Stack}: AngularJS, JavaScript, Go, Google Cloud App Engine, CSS, HTML
\end{rSubsection}

% \begin{rSubsection}{Music Kids}{Jul. 2013 - Sep. 2013}{Web Developer Intern}{Baltimore, MD}
% \item Led a team of interns and built a student attendance tracking and course scheduling system.
% \item Designed and implemented the full tech stack.
% \item \textbf{Technology}: jQuery, Ruby on Rails, Bootstrap, CoffeeScript, Less/CSS, Haml/HTML, MySQL, Git
% \end{rSubsection}

\end{rSection}

\begin{rSection}{Education}
{\bf Johns Hopkins University} \hfill {\bf Baltimore, MD} \\
{Master of Engineering in Computer Science} \hfill {Sept. 2012 - May 2014}

{\bf Fudan University} \hfill {\bf Shanghai, China} \\
{Bachelor of Science in Information Security} \hfill {Sept. 2008 - Jul. 2012}
\end{rSection}

\end{document}
