%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.35in,top=0.3in,right=0.35in,bottom=0.3in]{geometry} % Document margins

\name{Yifan Ge} % Your name
\address{34768 Swain Cmn., Fremont, CA 94555 \\ (408) 769-8746 \\ yifan.ge@outlook.com} % Your address
% \address{(408) 769-8746 \\ yifan.ge@outlook.com} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
{\bf Johns Hopkins University} \hfill {\bf Baltimore, MD} \\
{Master of Engineering in Computer Science} {\em GPA: 3.76/4.00} \hfill {Sept. 2012 - May 2014}

{\bf Fudan University} \hfill {\bf Shanghai, China} \\
{Bachelor of Science in Information Security} {\em Major GPA: 3.59/4.00} \hfill {Sept. 2008 - Jul. 2012}
\end{rSection}


%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{Google Inc.}{Nov. 2015 - Present}{Software Engineer}{Mountain View, CA}
\item Full-stack developer of Google Issue Tracker, a bug tracking tool used both internally across Google and externally to power open source projects.
\item Technical interviewer for Software Engineering roles.

\end{rSubsection}

\begin{rSubsection}{Motorola Mobility}{Jul. 2014 - Aug. 2015}{Software Engineer}{Sunnyvale, CA}
\item Full-stack developer and tech lead for the data analytics portal built on cloud platform using Golang and AngularJS.
\item Perform code reviewer for the broader team.
\item Technical interviewer for development roles.
\item 3rd place team winner of the 1st Motorola Global Hackathon across Bangalore, Chicago, Sao Paulo and Sunnyvale.
\end{rSubsection}

%------------------------------------------------

%% \begin{rSubsection}{Fudan University - Mobile Data Management Lab}{Sept. 2010 - Jul. 2012}{Reseach Assistant, Team Lead}{Shanghai, China}
%% \item Designed a quality-aware proactive service discovery protocol for Mobile Ad-hoc Networks.
%% \item Implemented and evaluated the protocol in a network simulator using C.
%% \item Analyzed the data and published two academic papers as 2nd authors in international conferences.
%% \end{rSubsection}

%------------------------------------------------
\end{rSection}

%----------------------------------------------------------------------------------------
%	PUBLICATIONS
%----------------------------------------------------------------------------------------

\begin{rSection}{Publications and Presentations}
{\bf Oral Presentation:} Xi Zhou; {\bf Yifan Ge}; Xuxu Chen; Yinan Jing; Weiwei Sun; , {\em `A Distributed Cache Based Reliable Service Execution and Recovery Approach in MANETs'}, The 6th IEEE International Conference on Asia-Pacific Services Computing Conference, Jeju-do, South Korea, Dec. 2011.

{\bf Poster Presentation:} Xi Zhou; {\bf Yifan Ge}; Xuxu Chen; Yinan Jing; Weiwei Sun; , {\em `SMF: A Novel Lightweight Reliable Service Discovery Approach in MANET'}, The 7th International Conference on Wireless Communications, Networking and Mobile Computing, Wuhan, China, Sept. 2011.
\end{rSection}

%----------------------------------------------------------------------------------------
%	SELECTED PROJECTS
%----------------------------------------------------------------------------------------
\begin{rSection}{Selected Projects}
\begin{rSubsection}{Social Networking Website (Course Project of Object Oriented Software Engineering)}{Fall 2013}{Team Lead}{Baltimore, MD}
% \item Course Project of {\em Object Oriented Software Engineering}.
\item Established a social networking featuring finer content organization. Posts are categorized into topics subscribed by the users.
% \item	Website constructed in a two-tier manner. Backend written in Ruby on Rails and frontend in AngularJS as a Single Page Application.
\item Conceived the concept of the project, initial database design and the project framework.
\item Initiated the backend APIs, implemented major parts of the frontend logic and user interface, and maintained project homepage and documentations.
\item Techniques used: Ruby on Rails, RSpec, Grunt, AngularJS, Bootstrap.
\end{rSubsection}
%--------------------------------
\begin{rSubsection}{Framework for Natural Interaction with Large Scaled Wall Displays}{Fall 2013}{Team Member}{Baltimore, MD}
\item Collaborated in the development of the software framework for a high resolution, 25 megapixel
display system which leverages the Robot Operating System (ROS) libraries to interface with Microsoft Kinect for gestural input.
\item Remodeled the existing app manager and built an extensible tooltip subsystem to support
multimedia for usage instructions.
\item Implemented a 3D menu based on Qt and OpenGL. Coded and trained human body gestures for VR
interactions with the menu.
\item Techniques used: Python, Qt, OpenGL, ROS.
\end{rSubsection}
%--------------------------------
\begin{rSubsection}{DSL for Programming Education (Course Project of Functional Programming at Work)}{Fall 2012}{Team Lead}{Baltimore, MD}
% \item Course Project of {\em Functional Programming at Work}.
\item Designed and developed a system for programming education through the form of a
side-scrolling game. The system reads the script input by the user, and translates it into the movements of the game character.
\item Game implemented in Haskell, SDL, and some other open source resources.
% \item Defined a state-machine-styled domain specific language to control the game character.
\item Techniques used: Haskell, SDL.
\end{rSubsection}
\end{rSection}
%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{3ex}} l }
Languages & Python, JavaScript, Golang, Ruby, C, C++, Java, Haskell, OCaml, Rust \\
Frameworks \& Platforms & AngularJS, Ruby on Rails, Google Cloud Platform \\
Tools & Linux, shell, git, Vim
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
